A Dependently Typed Multi-Stage Calculus \ifnotanonymous\thanks{Supported by organization x.}\fi

### 2019-06-15 text/formal-defnition.tex
Add an example of reduction sequence.
Revise Typing rules for a multi-stage calculus.

The relation $\longrightarrow_\beta$ represents ordinary $\beta-$reduction in the \(\lambda\)-calculus; the relation
$\longrightarrow_\blacklozenge$ represents that quotation $\TB_\alpha M$ is canceled by escape and $M$ is spliced into the code fragment surrounding the escape;
the relation $\longrightarrow_\Lambda$ means that a stage abstraction applied to the empty stage $\varepsilon$ reduces to the body of abstraction
where $\varepsilon$ is substituted for the stage variable.
There is no reduction rule for CSP as with Hanada and Igarashi \cite{Hanada2014}.
The CSP operator $\%_\alpha$ disappears when $\varepsilon$ is substituted to $\alpha$.
% $\TB_\alpha$ and $\TBL_\alpha$ disappears in the same way as $\%_\alpha$.

\AI{A few examples are desirable.}

@@

% Typing rules for a multi-stage calculus
\AI{This paragraph is not very informaticve.  We shouldn't just refer redears to previous work.}
The rules \TTB, \TTBL, \TGen, \TIns, and \TCsp{} are rules for a multi-stage calculus.
They are corresponding to brackets, escape, making a stage abstraction,
application of stage $A$ to a stage abstraction, and cross-stage persistence, respectively.
Please check Hanada and Igarashi \cite{Hanada2014} and Tsukada and Igarashi \cite{Tsukada} for details of these rules.

\begin{figure}
	\begin{center}
		\infrule[\TConst]{c:\tau \in \Sigma \andalso \G\V \tau::*@A}{\G \V c:\tau @A} \\[2mm]
		\infrule[\TVar]{x:\tau @A \in \G \andalso \G\V \tau::*@A}{\G \V x:\tau @A} \\[2mm]
		\infrule[\TAbs]{\G\V \sigma::*@A\andalso\G,x:\sigma@A\V M:\tau @A}{\G\V(\lambda (x:\sigma).M):(\Pi (x:\sigma).\tau)@A} \\[2mm]
		\infrule[\TApp]{\G\V M:(\Pi (x:\sigma).\tau)@A \andalso \G\V N:\sigma@A}{\G\V M\ N : \tau[x\mapsto N]@A} \\[2mm]
		\infrule[\TConv]{\G\V M:\tau @A \andalso \G\V \tau\equiv \sigma :: K@A}{\G\V M:\sigma@A} \\[2mm]
		\infrule[\TTB]{\G\V M:\tau @{A\alpha}}{\G\V\TB_{\alpha}M:\TW_{\alpha}\tau @A} \andalso
		\infrule[\TTBL]{\G\V M:\TW_{\alpha}\tau @A}{\G\V\TBL_{\alpha}M:\tau @{A\alpha}} \\[2mm]
		\infrule[\TGen]{\G\V M:\tau @A \andalso \alpha\notin\rm{FTV}(\G)\cup\rm{FTV}(A)}{\G\V\Lambda\alpha.M:\forall\alpha.\tau @A} \\[2mm]
		\infrule[\TIns]{\G\V M:\forall\alpha.\tau @A}{\G\V M\ \varepsilon:\tau[\alpha \mapsto \varepsilon]@A} \andalso
		\infrule[\TCsp]{\G\V M:\tau @A}{\G\V \%_\alpha M:\tau @{A\alpha}}
		\caption{Typing Rules.}
		\label{fig:typing-rules}
	\end{center}
\end{figure}

>>>>

The relation $\longrightarrow_\beta$ represents ordinary $\beta-$reduction in the \(\lambda\)-calculus; the relation
$\longrightarrow_\blacklozenge$ represents that quotation $\TB_\alpha M$ is canceled by escape and $M$ is spliced into the code fragment surrounding the escape;
the relation $\longrightarrow_\Lambda$ means that a stage abstraction applied to the empty stage $\varepsilon$ reduces to the body of abstraction
where $\varepsilon$ is substituted for the stage variable.
There is no reduction rule for CSP as with Hanada and Igarashi \cite{Hanada2014}.
The CSP operator $\%_\alpha$ disappears when $\varepsilon$ is substituted to $\alpha$.
We show an example of reduction sequence below.
Underlines show the redexes.
\begin{align*}
	 & \hspace{10mm} \underline{(\lambda i:\I\to\I.(\Lambda\alpha.\TB_\alpha (\%_\alpha i\ 1 + (\TBL_\alpha \TB_\alpha 3))\ \varepsilon))\ (\lambda x:\I.x)} \\
	 & \longrightarrow_\blacklozenge (\Lambda\alpha.\TB_\alpha (\%_\alpha (\lambda x:\I.x)\ 1 + (\underline{\TBL_\alpha \TB_\alpha 3})))\ \varepsilon        \\
	 & \longrightarrow_\beta \underline{(\Lambda\alpha.\TB_\alpha (\%_\alpha (\lambda x:\I.x)\ 1 + 3))\ \varepsilon}                                         \\
	 & \longrightarrow_\Lambda \underline{(\lambda x:\I.x)\ 1} + 3                                                                                           \\
	 & \longrightarrow_\beta 1 + 3                                                                                                                           \\
	 & \longrightarrow^* 4
\end{align*}

% $\TB_\alpha$ and $\TBL_\alpha$ disappears in the same way as $\%_\alpha$.

@@

% Typing rules for a multi-stage calculus
% \AI{This paragraph is not very informaticve.  We shouldn't just refer redears to previous work.}
The rules \TTB, \TTBL, \TGen, \TIns, and \TCsp{} are rules for a multi-stage calculus.
The rule \TTB{}, which corresponds to brackets, means that if term $M$ is of type $\tau$ at stage $A\alpha$,
$\TB_\alpha M$ is of type $\TW_\alpha \tau$ at stage $A$.
The rule \TTBL{}, which corresponds to escape, is the converse of \TTB.
The rule \TGen{} is a rule for stage abstraction.
The condition of $\alpha\notin\rm{FTV}(\G)\cup\rm{FTV}(A)$ ensure that
substitutions to $\alpha$ don't affect type environments or stages.
The rule \TIns{} is for applications of stages to stage abstractions.
The rule \TCsp is the rule for CSP, which means that 
if term $M$ is of type $\tau$ at stage $A$, $\%_\alpha M$ is of type $\tau$ at stage $A\alpha$.

\begin{figure}
	\begin{center}
		\infrule[\TConst]{c:\tau \in \Sigma \andalso \G\V \tau::*@A}{\G \V c:\tau @A} \\[2mm]
		\infrule[\TVar]{x:\tau @A \in \G \andalso \G\V \tau::*@A}{\G \V x:\tau @A} \\[2mm]
		\infrule[\TAbs]{\G\V \sigma::*@A\andalso\G,x:\sigma@A\V M:\tau @A}{\G\V(\lambda (x:\sigma).M):(\Pi (x:\sigma).\tau)@A} \\[2mm]
		\infrule[\TApp]{\G\V M:(\Pi (x:\sigma).\tau)@A \andalso \G\V N:\sigma@A}{\G\V M\ N : \tau[x\mapsto N]@A} \\[2mm]
		\infrule[\TConv]{\G\V M:\tau @A \andalso \G\V \tau\equiv \sigma :: K@A}{\G\V M:\sigma@A} \\[2mm]
		\infrule[\TTB]{\G\V M:\tau @{A\alpha}}{\G\V\TB_{\alpha}M:\TW_{\alpha}\tau @A} \andalso
		\infrule[\TTBL]{\G\V M:\TW_{\alpha}\tau @A}{\G\V\TBL_{\alpha}M:\tau @{A\alpha}} \\[2mm]
		\infrule[\TGen]{\G\V M:\tau @A \andalso \alpha\notin\rm{FTV}(\G)\cup\rm{FTV}(A)}{\G\V\Lambda\alpha.M:\forall\alpha.\tau @A} \\[2mm]
		\infrule[\TIns]{\G\V M:\forall\alpha.\tau @A}{\G\V M\ B:\tau[\alpha \mapsto B]@A} \andalso
		\infrule[\TCsp]{\G\V M:\tau @A}{\G\V \%_\alpha M:\tau @{A\alpha}}
		\caption{Typing Rules.}
		\label{fig:typing-rules}
	\end{center}
\end{figure}
